Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-30 algo_rank_harmony.Rmd
algo rank file with data update

 1. Suppose $C_1$ and $C_2$ are two cyclic granularities such that $C_1$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_I$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_M$\} and $v$ is the measured variable. Hence for each combination ($A_i$, $B_j$), we have s subset of the time series variable $v_{ij} \subseteq v$, $\forall i = {1, 2, \dots, I}$ and $\forall j = {1, 2, \dots, J}$

@@

```{r}
read_rds("cache/smart_harmony_ak.rds")
```

@@

 4.2. We have been able to normalize for the number of levels of x-axis variable using Step 3.2. Now 
$\forall A_i, \quad i \in \{1, 2, \dots, I\}$, we have $N_i = \frac{M_k - a_k}{b_k}$ each of which follows a standard Gumbel distribution. Now we need to combine these normalised variables across different facets in a way so that the number of facet levels do not play a role. For this we can take the mean, median or any quantiles of these normalised variables. But the median (and any quantiles) of these Gumbel distributions grow at the rate of (some power of) $log n$ with $n \xrightarrow{} \infty$. Hence, median($N_i$)/log($I$) could serve as the final measure.

```{r}
library(readr)
read_rds("cache/smart_harmony_musigma.rds")
```

## Version 3 (suggested by Sayani - old benchmark)

@@

```{r}
library(readr)
read_rds("cache/smart_harmony_n.rds")
```

>>>>

 1. Suppose $C_1$ and $C_2$ are two cyclic granularities such that $C_1$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_I$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_J$\} and $v$ is the measured variable. Hence for each combination ($A_i$, $B_j$), we have s subset of the time series variable $v_{ij} \subseteq v$, $\forall i = {1, 2, \dots, I}$ and $\forall j = {1, 2, \dots, J}$

@@

```{r}
read_rds("data/smart_harmony_ak.rds")
```

@@

 4.2. We have been able to normalize for the number of levels of x-axis variable using Step 3.2. Now 
$\forall A_i, \quad i \in \{1, 2, \dots, I\}$, we have a normalised variable each of which follows a standard Gumbel distribution. Now we need to combine these normalised variables across different facets in a way so that the number of facet levels do not play a role. For this we can take the mean, median or any quantiles of these normalised variables. But the median (and any quantiles) of these Gumbel distributions grow at the rate of (some power of) $log n$ with $n \xrightarrow{} \infty$. Hence, median($N_i$)/log($I$) could serve as the final measure.

```{r}
library(readr)
read_rds("data/smart_harmony_musigma.rds")
```

## Version 3 (old benchmark)

@@

```{r}
library(readr)
read_rds("data/smart_harmony_n.rds")
```

### 2020-04-30 main.Rmd
algo rank file with data update

```{r harmony-tab, echo=FALSE, cache=TRUE}
if(!dir.exists("cache/"))
{
  dir.create("cache")
}
if (!file.exists("cache/smart_harmony.rds")) {
  harmonies <- smart_meter10 %>%
  harmony(ugran = "month",
          filter_out = c("hhour", "fortnight"))

smart_harmony <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  rank_harmony(harmony_tbl = harmonies,response =  "general_supply_kwh")%>%
  rename(`facet variable` = facet_variable,
         `x-axis variable` = x_variable,
         `facet levels` = facet_levels,
         `x-axis levels` = x_levels,
         `average maximum variation` = mean_max_variation)

  write_rds(smart_harmony, "cache/smart_harmony.rds")
}
smart_harmony <- read_rds("cache/smart_harmony.rds")

>>>>

```{r harmony-tab, echo=FALSE, cache=TRUE}
if(!dir.exists("cache/"))
{
  dir.create("cache")
}
if (!file.exists("cache/smart_harmony.rds")) {
  sm <- smart_meter10 %>%
  filter(customer_id %in% c(10017936))

  harmonies <- sm %>%
  harmony(ugran = "month",
          filter_in = "wknd_wday", 
          filter_out = c("hhour", "fortnight"))

smart_harmony <- sm %>%
  rank_harmony(harmony_tbl = harmonies,response =  "general_supply_kwh")%>%
  rename(`facet variable` = facet_variable,
         `x-axis variable` = x_variable,
         `facet levels` = facet_levels,
         `x-axis levels` = x_levels,
         `average maximum variation` = mean_max_variation)

  write_rds(smart_harmony,"cache/smart_harmony_ak.rds")
}
smart_harmony <- read_rds("cache/smart_harmony.rds")
